Server-Side Probabilistic Programming

### 2018-11-06 abstract/paper.tex
measurements

>>>>

Table~\ref{tab:memory-runtime} provides memory consumption and
running time measurements on basic models to
illustrate  \texttt{infergo}'s performance.
The measurements were obtained on a 2.3GHz Intel Core 5
CPU with 8GB of memory for 1000 iterations of Hamiltonian Monte
Carlo with 10 leapfrog steps. Note that computation of log-likelihood
for standard distributions is not optimized yet. Quite the
opposite: since models in \texttt{infergo} are fully composable,
primitive distributions are themselves implemented as
\texttt{infergo} models and automatically differentiated.

\begin{table}[H]
	\caption{Memory and running times for 1000 iterations
	of HMC with 10 leapfrog steps.}
	\label{tab:memory-runtime}
	\begin{tabular}{r | c |  c | c}
		{\it model}  & \multicolumn{2}{c|}{\it time} & {\it memory} \\ 
		 & {\it compilation} & {\it execution} & \\\hline
		8 schools & 0.15s & 0.6s & 5.5MB \\
		10D normal, 100 points & 0.15s & 3.0s & 5.7MB \\
		50D normal, 100 points & 0.15s & 13.0s & 5.8MB 
	\end{tabular}
\end{table}
